Ms 1

### 2017-08-23 ms1/ms1_display.Rmd
ms1 cleanup

First, unadjusted trends in the number of diagnoses per 1,000 beneficiaries in each year:

```{r dx_counts}
read_tsv('tables/dx_counts.tsv') %>%
  select(diagnosis_category, year, dxpkp) %>%
  filter(year %in% c(2011, 2014)) %>%
  spread(year, dxpkp) %>%
  mutate(pct_change=(`2014`/`2011`-1)*100) %>%
  arrange(desc(`2011`)) %>%
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  kable
```

### Adjusted trends in diagnoses

@@

```{r dx_trends_adjusted}
read_tsv('tables/dx_models.tsv') %>%
  filter(term=='year0') %>%
  mutate(pct_change=100*(exp(estimate*3)-1),
         p.value=p.adjust(p.value, method='BH')) %>%
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  select(diagnosis_category, pct_change, p.value) %>%
  kable
```

@@

For each drug, I asked what fraction of PDEs are associated with each diagnosis. This gives you a sense that, say, the diagnoses that give rise to azithromycin are bronchitis, URI, etc. The values are percents. I might display just the 2011 data in the paper.

```{r pde_dx}
read_tsv('tables/pde_dx_counts.tsv') %>%
  filter(antibiotic %in% top_abx, year %in% c(2011, 2014)) %>%
  rename(pct=f_pde_with_dx) %>%
  select(antibiotic, year, diagnosis_category, pct) %>%
  spread(year, pct) %>%
  mutate(pct_change=`2014`/`2011`-1) %>%
  gather('key', 'value', c('2011', '2014', 'pct_change')) %>%
  mutate(value=round(value*100, 1)) %>%
  spread(diagnosis_category, value) %>%
  kable
```

@@

For each diagnosis and each drug, I ask what fraction of diagnoses are followed by a PDE for that drug.

```{r dx_pde}
read_tsv('tables/dx_pde_counts.tsv') %>%
  filter(antibiotic %in% top_abx, year %in% c(2011, 2014)) %>%
  rename(pct=f_dx_with_pde) %>%
  select(antibiotic, year, diagnosis_category, pct) %>%
  spread(year, pct) %>%
  mutate(pct_change=`2014`/`2011`-1) %>%
  gather('key', 'value', c('2011', '2014', 'pct_change')) %>%
  mutate(value=round(value*100, 1)) %>%
  spread(diagnosis_category, value) %>%
  kable
```

### Adjusted trends

These are logistic regressions. The unit of analysis is the diagnosis. The outcome is whether a PDE for that drug follows a diagnosis in that category. The main predictor is year; covariates are as above. The odds ratio is between 2011 and 2014. I'll convert that into a risk ratio using the 2011 probabilities from the previous table.

```{r dx_pde_adjusted}
read_tsv('tables/dx_pde_model.tsv') %>%
  filter(term=='year0') %>%
  mutate(p.value=p.adjust(p.value, method='BH'),
         OR=round(exp(3*estimate), 2)) %>%
  filter(p.value < 0.05) %>%
  select(antibiotic, diagnosis_category, OR) %>%
  spread(diagnosis_category, OR) %>%
  head %>%
  kable
```

>>>>

First, unadjusted trends in the number of diagnoses per 1,000 beneficiaries in each year. The percent change is between 2011 and 2014.

@@

```{r dx_trends}
dx_unadj = read_tsv('tables/dx_counts.tsv') %>%
  select(diagnosis_category, year, dxpkp) %>%
  filter(year %in% c(2011, 2014)) %>%
  spread(year, dxpkp) %>%
  mutate(unadj_pct_change=(`2014`/`2011`-1)*100) %>%
  arrange(desc(`2011`)) %>%
  mutate_if(is.numeric, function(x) round(x, 2))

dx_adj = read_tsv('tables/dx_models.tsv') %>%
  filter(term=='year0') %>%
  mutate(adj_pct_change=100*(exp(estimate*3)-1),
         p.value=p.adjust(p.value, method='BH')) %>%
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  select(diagnosis_category, adj_pct_change, p.value)

full_join(dx_unadj, dx_adj, by='diagnosis_category') %>%
  kable
```

@@

For each drug, I asked what fraction of PDEs are associated with each diagnosis. This gives you a sense that, say, the diagnoses that give rise to azithromycin are bronchitis, URI, etc. The values are percents in 2011.

The first table includes a "no diagnosis" category. This means that the majority of PDEs were not downstream of a diagnosis. In the second table, I remove the "none" diagnosis and rescale the values, which helps make it easier to read.

```{r pde_dx}
read_tsv('tables/pde_dx_counts.tsv') %>%
  filter(antibiotic %in% top_abx, year==2011) %>%
  mutate(pct=round(f_pde_with_dx*100, 1)) %>%
  select(antibiotic, diagnosis_category, pct) %>%
  spread(diagnosis_category, pct) %>%
  kable

read_tsv('tables/pde_dx_counts.tsv') %>%
  filter(antibiotic %in% top_abx, year==2011, diagnosis_category != 'none') %>%
  group_by(antibiotic) %>%
  mutate(f=f_pde_with_dx/sum(f_pde_with_dx),
         pct=round(f*100, 1)) %>%
  ungroup() %>%
  select(antibiotic, diagnosis_category, pct) %>%
  spread(diagnosis_category, pct) %>%
  kable
```

@@

For each diagnosis and each drug, I ask what fraction of diagnoses are followed by a PDE for that drug in 2011 and 2014. I compute the percent change in those fractions.

Second, I do logistic regressions. The unit of analysis is the diagnosis. The outcome is whether a PDE for that drug follows a diagnosis in that category. The main predictor is year; covariates are as above. The odds ratio is between 2011 and 2014. (I'll convert that into a risk ratio using the 2011 probabilities.)

```{r dx_pde_trends}
dx_pde_unadj = read_tsv('tables/dx_pde_counts.tsv') %>%
  filter(antibiotic %in% top_abx, year %in% c(2011, 2014)) %>%
  mutate(key=str_c('y', year)) %>%
  select(diagnosis_category, antibiotic, key, value=f_dx_with_pde)

dx_pde_adj = read_tsv('tables/dx_pde_model.tsv') %>%
  filter(term=='year0') %>%
  mutate(key='OR',
         p.value=p.adjust(p.value, method='BH'),
         OR=round(exp(3*estimate), 2)) %>%
  filter(p.value < 0.05) %>%
  select(diagnosis_category, antibiotic, key, value=OR)

# risk ratio
rr = function(odds_ratio, p0) odds_ratio / (1 - p0 + (p0 * odds_ratio))

 bind_rows(dx_pde_unadj, dx_pde_adj) %>%
   spread(key, value) %>%
   mutate(pct_change=(y2014/y2011-1)*100,
          adj_pct_change=(rr(OR, y2011)-1)*100) %>%
   select(-OR) %>%
   #mutate_if(is.numeric, function(x) round(x, 2)) %>%
   gather('key', 'value', y2011:adj_pct_change) %>%
   mutate(value=round(value, 2)) %>%
   spread(diagnosis_category, value) %>%
   mutate(key=factor(key, levels=c('y2011', 'y2014', 'pct_change', 'adj_pct_change'))) %>%
   arrange(antibiotic, key) %>%
   kable
```
